---
title: "Module 4. Simple Linear Regression. Advertising case"
author: "I. Maslova"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

Suppose are hired a data science consultants hired by a client to provide advice on how to improve sales of a particular product. It is not possible for our client to directly increase sales of the product. On the other hand, they can control the advertising expenditure in each of the three media. Therefore, if we determine that there is an association between advertising and sales, then we can instruct our client to adjust advertising budgets, thereby indirectly increasing sales. In other words, our goal is to develop an accurate model that can be used to predict sales on the basis of the three media budgets.

•	Which media contribute to sales?
•	Which media generate the biggest boost in sales? or
•	How much increase in sales is associated with a given increase in TV advertising?

What information would be useful in order to provide such a recommendation? Here are a few important questions that we might seek to address:

Data: 

The Advertising data set consists of the sales ( in thousands of units) of that product in 200 different markets, along with advertising budgets (in thousands of dollars) for the product in each of those markets for three different media: TV, radio, and newspaper. 

 Business questions: 

Is there a relationship between advertising budget and sales?

Our first goal should be to determine whether the data provide evidence of an association between advertising expenditure and sales. If the evidence is weak, then one might argue that no money should
be spent on advertising!

How strong is the relationship between advertising budget and sales?

Assuming that there is a relationship between advertising and sales, we would like to know the strength of this relationship. In other words, given a certain advertising budget, can we predict sales with a high level of accuracy? This would be a strong relationship. Or is a prediction of sales based on advertising expenditure only slightly better than a random guess? This would be a weak relationship.

Which media contribute to sales?
Do all three media—TV, radio, and newspaper—contribute to sales, or do just one or two of the media contribute? To answer this question, we must find a way to separate out the individual effects of each medium when we have spent money on all three media.

How accurately can we estimate the effect of each medium on sales?
For every dollar spent on advertising in a particular medium, by what amount will sales increase? How accurately can we predict this amount of increase?

How accurately can we predict future sales?
For any given level of television, radio, or newspaper advertising, what is our prediction for sales, and what is the accuracy of this prediction?

Is the relationship linear?
If there is approximately a straight-line relationship between advertising expenditure in the various media and sales, then linear regression is an appropriate tool. If not, then it may still be possible to transform the predictor or the response so that linear regression can be used.

Is there synergy among the advertising media?
Perhaps spending $50,000 on television advertising and $50,000 on radio advertising results in more sales than allocating $100,000 to either television or radio individually. In marketing, this is known as a synergy effect, while in statistics it is called an interaction effect.


Technical note: linear regression can be used to answer each of these questions.

@.	Set working directory.

@.	Import data in R.

```{r}
data<-read.csv("Advertising(2).csv", header=T)
```



@.	Display first 4 rows and last 3 rows of data.

```{r}
head(data,4)
tail(data,3)
```

@.	How many rows and columns does your data table have?
```{r}
dim(data)
```


@.	What are the names of columns in the data table?
```{r}
names(data)
```



@.	In regression context how can we refer to variable Y? Provide at least two different names for Y.

TV
```{r}

```


@.	In regression context how do we call variable X? Provide at least two different names for X.


@.	Write down a model to predict the sales from the TV advertising budget. Express your model using variable names.

predicted Sales = intercept+ slope*TV advertising budget

@.	Create a scatter plot: sales versus TV advertising expenditures. Comment on the pattern.
```{r}
attach(data)
plot(TV, sales, main = "Scatterplot of TV advertising budget vs Sales")

plot(log(TV),sales)
plot(log(TV),log(sales))

```
approximately linear, but there are some issues:
@. Fit the regression model to predict sales based on TV advertising.
```{r}
m= lm(sales~TV)
m
```

@. Is the association between the sales and TV advertising significant?
```{r}
summary(m)
```

@. Are the model assumptions met?
```{r}
plot(m)
library(forecast)
Acf(m$residuals)
```

