---
title: "Lab 3. Forecasting Shampoo Sales"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Shampoo sales case

The file ShampooSales.xls contains
data on the monthly sales of a certain shampoo over a 3-year
period. (source: Hyndman, R. J. Time Series Data Library,
http://data.is/TSDLdemo; accessed on July 13, 2015.)

(@) Download the data and convert it to a ts object called _data.ts_.
```{r}
install.packages("readxl")
library(readxl)

data=read_excel("ShampooSales.xls")
head(data)

data.ts=ts(data$`Shampoo Sales`, start = c(1995,1), frequency = 12)

```

(@) Create a well-formatted time plot of the data. Use _library(forecast)_ and _autoplot()_ function.

```{r}

library(forecast)
autoplot(data.ts)

```


(@) Which of the four components (level, trend, seasonality,
noise) seem to be present in this series?

```{r}

```


(@) Do you expect to see seasonality in sales of shampoo?
Why?
```{r}

```

(@) Use _window()_ function with options *start=c(start year, start month)* and *end= c(end year, end month)* to partition data into training (call it _train.ts_) and validation series (call it _valid.ts_). Let the training set consist of the first 2 years of data and validation set be the last year of the time series data. Report the script you used on BB.
```{r}

start(data.ts)
end(data.ts)

train.ts = window(data.ts, end=c(1996,12), frequency = 12)
valid.ts = window(data.ts, start = c(1997,1))

```


(@) Use the _tslm()_ function and fit the model to the training ( _train.ts_ ) data. Include the components (trend, seasonal that you've identified earlier). Create the plot of observed values and the fitted values using _autoplot()+autolayer()_ functions.
Does it look like a goot fit (based on the visual analysis)?
```{r}
model = tslm(train.ts~trend + season)
autoplot(train.ts)+
  autolayer(model$fitted.values)

```

(@) Use function _accuracy(train.ts, ModelName$fitted.values)_ function and report the RMSE on the training set.
```{r}
accuracy(train.ts, model$fitted.values)
```

(@) Next, forecast shampoo sales 12 months ahead using _forecast()_ function. Report the forecasted sales on December 1997.

```{r}
pred=forecast(model, h=12)
pred

```

(@) Use the _accuracy()_ function to report the prediction RMSE (RMSE on the testing set).
```{r}
accuracy(valid.ts, pred$mean)
```


(@) Did the testing RMSE increase from the training RMSE?

