---
title: "Week 4. Classical decomposition"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Creating a time series object in R

```{r}
tmp<- c(1:100)+rnorm(100, mean=0, sd=5)

plot.ts(tmp)

class(tmp)

tmp.ts<-ts(tmp, start=c(2022, 1), frequency = 12)

class(tmp.ts)
plot(tmp.ts)

```


 We will be looking at the `AirPassengers` dataset 
 which comes with the `forecast` package. This means 
 that you don't have to read it from an external csv file. 
 The data has the monthly totals (in thousands) of 
 international airline passenger bookings, 1949 to 1960. 
 Let's go ahead and see what is in this time series dataset: 
 
```{r}  
#load the forecast R package
install.packages("forecast")
library(forecast)

```

Let's have a look at the data set

```{r}

```

Convert data from monthly to yearly using \verb{aggregate()} function. Check whether there is seasonality present.

```{r}

```


### Time series components

How to estimate the components in practice? Start with linear trend. Check whether it is a good fit.Analyze the residuals. Check the assumptions of the linear model to decide whether further decomposition is needed.

```{r}

```



Next, try quadratic trend. Fit the model, add the quadratic trend line, evaluate the fit. Analyze the residuals.

```{r}

```

Estimate the seasonal component. Add the fitted model,evaluate the fit. Analyze the residuals.

```{r}

```



What about multiplicative model? How should we modify the previous analysis to get it?

```{r}

```

