---
title: "AB testing"
author: "Y.Sun"
date: "2022-09-19"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

To run an AB test we need to set up hypothesis first. 

\vspace{2mm}

Null: B is not better than A. Decision: do nothing.

Alternative: B is better than A, some practical action will follow.


Choose the significance level $\alpha$. Usually it is 1, 5, or 10 percent. It is the probability of type 1 error, i.e. chance that we reject the null, when in reality it is true. Chances that we have switched to version B unnecessarily.

Decision rule: if $p-value \leq \alpha$, reject the null, conclude the alternative. Otherwise, we fail to reject the null, and we do nothing. 

##Barbie vs. Bratz

Null: The 7-year-olds DO NOT identify more strongly with the Duff Barbie in Stuff than the Bratz.

Alternative: The 7-year-olds identify more strongly with the Duff Barbie in Stuff than the Bratz. Average score for Barbie > average score for Bratz.

```{r}
data=read.table("BarbievsBratz.txt", header=TRUE)
head(data,2)

t.test(data$DuffBarbie, data$BratzDoll, 
       alternative = "greater")

```

Since p-value is greater than 5 percent, fail to reject the null. Conclude that Barbie doll is not better than Bratz.







